Who does big team science?

### 2023-04-20 manuscript_scopus.Rmd
small typo fixes

@@

ggplot(DF$inst_time %>% 
         filter(SubjectArea != "Multidisciplinary") %>% 
         mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))), 
       aes(Decade, `normalized`)) + 
  #geom_point() + 
  geom_violin() + 
  theme_classic() + 
  facet_wrap(~SubjectArea) + 
  ylab("Percent of Unique Affiliations") + 
  xlab("Decade")
```

@@

# tree map
DF$geo_country$un_region_sub <- countrycode(
  sourcevar = DF$geo_country$affiliation_tag_country,
  origin = 'iso3c', 
  destination = 'un.regionsub.name'
)

DF$geo_country$un_region <- countrycode(
  sourcevar = DF$geo_country$affiliation_tag_country,
  origin = 'iso3c', 
  destination = 'un.region.name'
)

@@

```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions and variance in the number of regions represented in big-team science publiactions predicting time and the overall mode effect size."}
label <- c("Physical", "Social", "Health", "Life")
b_values <- c(-0.061001, -0.077040, -0.017775, -0.014946)
se_values <- c(0.022958, 0.058153, 0.009794, 0.010485)
r2_values <- c(0.002357, 0.004491, 0.000434, 0.000434)
sample_size <- 13000

@@

@@

```{r author-gpe-figure, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades."}
small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
medium_author + ggtitle("50-99 Authors") + #theme(legend.position = "none") + 
large_author + ggtitle("100 + Authors") + #theme(legend.position = "none") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

>>>>

strip_labels_2 <- expression(
  "Coefficient" = b,
  "Effect Size" = R^2
)

@@

picture <- ggplot(DF$inst_time %>% 
         filter(SubjectArea != "Multidisciplinary") %>% 
         mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))), 
       aes(Decade, `normalized`)) + 
  #geom_point() + 
  geom_violin() + 
  theme_classic() + 
  facet_wrap(~SubjectArea) + 
  ylab("Percent of Unique Affiliations") + 
  xlab("Decade")

suppressWarnings(print(picture))
```

@@

# tree map
DF$geo_country$un_region_sub <- suppressWarnings(
  countrycode(
  sourcevar = DF$geo_country$affiliation_tag_country,
  origin = 'iso3c', 
  destination = 'un.regionsub.name')
)

DF$geo_country$un_region <- suppressWarnings(
  countrycode(
  sourcevar = DF$geo_country$affiliation_tag_country,
  origin = 'iso3c', 
  destination = 'un.region.name')
)

@@

```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}
label <- c("Physical", "Social", "Health", "Life")
b_values <- c(-0.061001, -0.077040, -0.017775, -0.014946)
se_values <- c(0.022958, 0.058153, 0.009794, 0.010485)
r2_values <- c(0.002357, 0.004491, 0.000434, 0.000434)
sample_size <- 13000

@@

# graph_data$type <- factor(
#   graph_data$type, 
#   levels = c("Coefficient", "Effect Size")
# )

ggplot(graph_data, aes(label, estimate)) + 
  geom_point() +
  geom_pointrange(aes(ymin = low, ymax = high)) +
  theme_classic() + 
  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels_2))) + 
  geom_hline(yintercept = 0) + 
  coord_flip() + 
  xlab("Subject Area") + 
  ylab("")
```

@@

```{r author-gpe-figure, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors."}
small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
medium_author + ggtitle("50-99 Authors") + #theme(legend.position = "none") + 
large_author + ggtitle("100 + Authors") + #theme(legend.position = "none") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

### 2023-04-20 manuscript_scopus.tex
small typo fixes

\begin{verbatim}
## Warning: Groups with fewer than two data points have been dropped.
## Groups with fewer than two data points have been dropped.
## Groups with fewer than two data points have been dropped.
\end{verbatim}

@@

\begin{verbatim}
## Warning in countrycode_convert(sourcevar = sourcevar, origin = origin, destination = dest, : Some values were not matched unambiguously: ANT, EUE, TWN

## Warning in countrycode_convert(sourcevar = sourcevar, origin = origin, destination = dest, : Some values were not matched unambiguously: ANT, EUE, TWN
\end{verbatim}

@@

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-diversity-1.pdf}
\caption{\label{fig:fig-diversity}Number of geopolitical regions and variance in the number of regions represented in big-team science publiactions predicting time and the overall mode effect size.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/author-gpe-figure-1.pdf}
\caption{\label{fig:author-gpe-figure}A comparison of author affiliation geopolitical region across decades.}
\end{figure}

>>>>

@@

@@

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-diversity-1.pdf}
\caption{\label{fig:fig-diversity}Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/author-gpe-figure-1.pdf}
\caption{\label{fig:author-gpe-figure}A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors.}
\end{figure}
